From Archives to AI: Residential Property Data Across Three Decades in Brunei Darussalam

### 2025-02-22 manuscript.qmd
Update manuscript

>>>>

## LLM Accuracy Test

To test the accuracy of the LLM data cleaning, we created a test data set of 100 house advertisements in the style of the web scraped data.
Several popular models from Ollama were used, namely the Llama 3.2 (3B), Mistral (7B), Phi4 (14B), and DeepSeek-R1 distilled reasoning models based on Llama (8B) and Qwen (14B).
Additionally, two models from OpenAI were included for comparison. 
These were the GPT-4o and the o1-mini, with the latter being a reasoning model.

The metric used to assess accuracy is a similarity measure within a tolerance of 1% of the true value. 
For numeric variables, the absolute difference is used.
For non-numeric variables, the normalised Levenshtein distance is used.
The code to replicate the analysis is available on the GitHub repository.

The results show that reasoning models outperform the non-reasoning models, with OpenAI's o1-mini model performing the best (98.2% accuracy) followed by the locally run deepseek-r1:14b Ollama model (92.5% accuracy).
Most inaccuracies are seen in the `status` variable, where the models had a difficult time parsing the correct build status from the advertisement.
However, key variables such as `price`, `type`, `plot_area`, `floor_area`, `beds`, and `baths` are generally reliable (>90% accuracy).

{{< embed analysis.qmd#fig-llmtest >}}

The run time statistics for each model is shown in the table below.
Running OpenAI's models are much faster than running models locally, though a paid API key is required.

```{r}
#| label: tbl-llmtest-time
#| tbl-cap: Single run time statistics for LLM data cleaning for each model in seconds.
llmtest_time <-
  tibble(
    model = c("llama3.2", "mistral", "phi4", "deepseek-r1:8b", "deepseek-r1:14b", "gpt-4o", "o1-mini"),
    min = c(4.705968, 2.695677, 7.763636, 49.028515, 97.197804, 1.279267, 5.968378),
    mean = c(6.136084, 8.385252, 21.278234, 77.494729, 146.424187, 2.457973, 7.945925),
    median = c(6.278579, 9.302804, 25.710515, 69.055948, 149.651830, 1.733497, 7.506522),
    max = c(7.830766, 13.328297, 28.309253, 138.477761, 212.098819, 5.379483, 9.943231)
  )

gt(llmtest_time) |>
  fmt_number(decimals = 2) |>
  cols_label(
    model = "Model",
    min = "Minimum",
    mean = "Mean",
    median = "Median",
    max = "Maximum"
  ) |>
  tab_spanner(
    label = "Time (seconds)",
    columns = min:max
  )
```

<!-- Unit: seconds -->
<!--             expr       min         lq       mean     median         uq        max neval cld -->
<!--         llama3.2  4.705968   5.343346   6.136084   6.278579   6.521761   7.830766     5 a   -->
<!--          mistral  2.695677   4.423615   8.385252   9.302804  12.175866  13.328297     5 a   -->
<!--             phi4  7.763636  17.141029  21.278234  25.710515  27.466739  28.309253     5 a   -->
<!--   deepseek-r1:8b 49.028515  53.375558  77.494729  69.055948  77.535864 138.477761     5  b  -->
<!--  deepseek-r1:14b 97.197804 119.387742 146.424187 149.651830 153.784741 212.098819     5   c -->
<!--           gpt-4o  1.279267   1.502509   2.457973   1.733497   2.395108   5.379483     5 a   -->
<!--          o1-mini  5.968378   6.551901   7.945925   7.506522   9.759592   9.943231     5 a   -->
